---
title: "Exam"
description: |
  What have you learned?
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

![Exams are learning instruments too... <br> <span>photo by <a href="https://unsplash.com/@anniespratt?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">Annie Spratt</a> on <a href="https://unsplash.com/s/photos/test?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">Unsplash</a></span>](photos/annie-spratt-JexAuNCfefs-unsplash.jpg)

# Assessment

The assessment will take place 22.5.23, 14:15-15:45 and will consist of an in-person multiple-choice exam. 

The exam will be implemented on EvaExam and students will be asked to bring their own devices (BYOD principle) to complete the exam. 

We will have a practice trial with this system on 24.04.23. Those students who experience problems during the practice trial or prefer a paper-pencil version of the exam should make a direct request to the instructor at least 2 weeks before the final exam date (22.5.23). 

```{r, include=FALSE}
# The exam will take place over EvaExam on 25.05.2021, between 16:15 and 17:45. Additional information about the EvaExam system will be provided closer to the exam date.
# 
# The grades will be communicated by email about two weeks after the exam (i.e., 07.06.2021) and students who would like to view their exam results should write an email to the instructor to communicate that they will attend the in-person meeting scheduled for 15.06.2021 (16:00-17:00). 
# 
# ### Multiple choice questions
# 
# Multiple-choice questions will be of the type K-Prim: No correct answer, or several correct answers.
# 
# Each question or incomplete statement is followed by four possible responses or statements. For each response or statement, a decision must be made as to whether it is right or wrong. Regardless of whether the question is grammatically formulated in the singular or the plural, one, two, three, four or even none of the answers may be correct. For each question, four correct answers equal 1 point, three correct equal .5 points, and less than 3 correct answers equal 0 points.
```
